Using SIMD and SIMT vectorization to evaluate sparse chemical kinetic Jacobian matrices and thermochemical source terms

### 2018-08-09 paper.tex
s/achievements/efforts

\add{These achievements are made publicly available (see~\cref{A:availability}) via the open-source, high-performance, chemical kinetics code \texttt{pyJac}}.
The new molar-based formulation \delete{for \texttt{pyJac}} resulted in highly sparse chemical kinetic Jacobians, and allows selection of either the constant-volume or constant-pressure approximation.
In addition, sparsity can be increased further by eliminating components associated with the bath gas, as discussed in \cref{S:sparsity}; this approximation is not a key feature of this work, and future efforts to \revisedelete{develop}\revise{incorporate} more sophisticated Jacobian approximations\delete{ based on the \texttt{pyJac} software} would be a worthwhile endeavor.

>>>>

\add{These efforts are made publicly available (see~\cref{A:availability}) via the open-source, high-performance, chemical kinetics code \texttt{pyJac}}.
The new molar-based formulation \delete{for \texttt{pyJac}} resulted in highly sparse chemical kinetic Jacobians, and allows selection of either the constant-volume or constant-pressure approximation.
In addition, sparsity can be increased further by eliminating components associated with the bath gas, as discussed in \cref{S:sparsity}; this approximation is not a key feature of this work, and future efforts to \revisedelete{develop}\revise{incorporate} more sophisticated Jacobian approximations\delete{ based on the \texttt{pyJac} software} would be a worthwhile endeavor.
